---
output: html_document
editor_options: 
  chunk_output_type: console
---
## Results {#sep-results}

```{r}
cols = list(
  solid = c(Separated = "royalblue"),
  transparent = scales::alpha(c(Separated = "royalblue"), 0.4)
)
```

**Notation:**

-   Text that describes figure notation and that could be found in a figure caption is formatted as regular text.
-   *Text that describes the interpretation of results to make inference is formatted as italic text.*
-   All credible intervals are equal-tailed, all point estimates are posterior medians, and all shaded regions are 95% credible intervals.
-   All boxplots show 95% credible limits as whiskers, 50% credible limits as boxes, and posterior medians as the heavy line. Horizontal dotted lines on boxplot figures are posterior means across all samples and populations.
-   If a quantity is shown without uncertainty, it is the posterior median.
-   Populations are ordered by approximate distance up-river, from downstream to upstream. 

```{r Global setup, include = F}
# CRAN packages
library(reshape2)
library(mvtnorm)
library(scales)
library(knitr)
library(kableExtra)
library(dplyr)
library(coda)
library(stringr)
library(postpack)

# load functions
source("../fit-integrated-model/functions.R")
```

```{r load posterior samples, message = F}
# load in the posterior samples
post = readRDS(file = "../posterior-samples/seperated-posterior.rds")

# fix variable names: some one-dimensional objects have two dimensions in variable name
colnames(post)[colnames(post) %in% paste0("alpha[1,", 1:8, "]")] = paste0("alpha[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("beta[1,", 1:8, "]")] = paste0("beta[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("D.sum[1,", 1:8, "]")] = paste0("D.sum[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("S.msy[1,", 1:8, "]")] = paste0("S.msy[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("U.msy[1,", 1:8, "]")] = paste0("U.msy[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("sigma.R[1,", 1:8, "]")] = paste0("sigma.R[", 1:8, "]")
colnames(post)[colnames(post) %in% paste0("lnalpha[1,", 1:8, "]")] = paste0("lnalpha[", 1:8, "]")

# place abundance quantities on fish scale, not thousands of fish
post[,str_detect(colnames(post), "^S\\[")] = post[,str_detect(colnames(post), "^S\\[")] * 1000
post[,str_detect(colnames(post), "^C\\[")] = post[,str_detect(colnames(post), "^C\\[")] * 1000
post[,str_detect(colnames(post), "^R\\[")] = post[,str_detect(colnames(post), "^R\\[")] * 1000
post[,str_detect(colnames(post), "^beta\\[")] = post[,str_detect(colnames(post), "^beta\\[")] / 1000
post[,str_detect(colnames(post), "^N\\[")] = post[,str_detect(colnames(post), "^N\\[")] * 1000
post[,str_detect(colnames(post), "^S\\.msy\\[")] = post[,str_detect(colnames(post), "^S\\.msy\\[")] * 1000

# coerce to mcmc.list
post = post_convert(post)

# rename misc quantities for consistency with integrated ssm
post_rename = function(post, param_original, param_new) {
  
  matches = match_params(post, param_original)
  post_m = as.matrix(post, chains = T, iters = T)
  which_matches = which(colnames(post_m) %in% matches)
  
  original_base = stringr::str_remove_all(param_original, "[\\^\\[]")
  
  colnames(post_m)[which_matches] = stringr::str_replace(colnames(post_m)[which_matches], original_base, param_new)
  
  post_convert(post_m)
}

post = post_rename(post, "D.sum", "D_sum")
post = post_rename(post, "^sigma.R[", "sigma_R")
post = post_rename(post, "S.msy", "S_msy")
post = post_rename(post, "U.msy", "U_msy")
post = post_rename(post, "^q", "q_stock")
post = post_rename(post, "^log.resid[", "log_resid")

post = post_remove(post, "lnalpha", F)

# re-order populations for consistency with main-text figures
# White-Donjek needs to come right after LwrMain and before Stewart and Pelly
#old = get_params(post, type = "base_index")
#new = old

#new[str_detect(old, "\\[2\\]")] = str_replace(old[str_detect(old, "\\[2\\]")], "\\[2\\]", "[3]")
#new[str_detect(old, "\\[3\\]")] = str_replace(old[str_detect(old, "\\[3\\]")], "\\[3\\]", "[4]")
#new[str_detect(old, "\\[4\\]")] = str_replace(old[str_detect(old, "\\[4\\]")], "\\[4\\]", "[2]")
#new[str_detect(old, ",2\\]$")] = str_replace(old[str_detect(old, ",2\\]$")], ",2\\]$", ",3]")
#new[str_detect(old, ",3\\]$")] = str_replace(old[str_detect(old, ",3\\]$")], ",3\\]$", ",4]")
#new[str_detect(old, ",4\\]$")] = str_replace(old[str_detect(old, ",4\\]$")], ",4\\]$", ",2]")

#x = as.matrix(post)
#colnames(x) = new
#x = x[,sort(colnames(x))]
#post = post_convert(cbind(postpack:::id_mat(post), x))
```

```{r load data}
in_dir = "../fit-integrated-model/inputs"
C_file = "catch-data.csv"
S_file = "esc-data.csv"
A_file = "age-data.csv"

# read in the raw data files
S_dat = read.csv(file.path(in_dir, S_file), stringsAsFactors = F)
age_dat = read.csv(file.path(in_dir, A_file), stringsAsFactors = F)
H_dat = read.csv(file.path(in_dir, C_file), stringsAsFactors = F)

# re-order populations for consistency with main-text figures
# White-Donjek needs to come right after LwrMain and before Stewart and Pelly
#top = S_dat[S_dat$stock %in% "LwrMain",]
#shift = S_dat[S_dat$stock %in% "White-Donjek",]
#bottom = S_dat[!(S_dat$stock %in% c("LwrMain", "White-Donjek")),]
#S_dat = rbind(top, shift, bottom)

#top = age_dat[age_dat$stock %in% c("aggregate", "LwrMain"),]
#shift = age_dat[age_dat$stock %in% "White-Donjek",]
#bottom = age_dat[!(age_dat$stock %in% c("aggregate", "LwrMain", "White-Donjek")),]
#age_dat = rbind(top, shift, bottom)

# prepare the data files
inputs = raw_data_prep(
  S_dat = S_dat,
  H_dat = H_dat,
  age_dat = age_dat
)

# separate them into observed and params (params are pretty much all dimensions)
obs = inputs$obs
params = inputs$params
attach(params)

# create broodtables and get brood year recruitment by stock
obs = gen_Rys_obs(params = params, obs = obs)

# get year and brood year names
years = as.numeric(rownames(obs$S_ts_obs))
brood_years = (min(years) - 7):(max(years) - 4)
```

```{r}
mcmc_statement = "**The MCMC diagnostic summaries in this section are from the eight separate models.**"
```

```{r, eval = T, child = "chunks-convergence.Rmd"}
```

### Key Posterior Estimates {.tabset .tabset-pills}

```{r my-boxplot-function}
my_boxplot = function(param, ylab, cols, by_1000 = F, ...) {
  # set graphics params
  my_par(mar = c(4.5,3.5,0.25,0.25))
  
  # extract the summary
  param_post = post_subset(post, param, matrix = T)
  if (by_1000) param_post = param_post/1000
  mean_param = mean(param_post)
  param_summ = apply(param_post, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  stats = boxplot(param_post, plot = F)
  stats$stats = param_summ
  bxp(stats, outline = F, xaxt = "n", ylab = ylab, las = 1, plot = F,
      whisklty = 1, whisklwd = 2, whiskcol = cols$solid,
      staplelty = 0, staplecol = cols$solid,
      boxcol = cols$solid, boxlwd = 2, boxfill = cols$transparent,
      medcol = cols$solid, medlwd = 3
  )
  abline(h = mean_param, col = cols$solid, lty = 3, lwd = 2)
  usr = par("usr")
  axis(side = 1, at = 1:ns, labels = rep("", ns))
  text(x = 1:ns + 0.25, y = usr[3] - (usr[4] - usr[3]) * 0.03, labels = stocks, srt = 45, xpd = T, pos = 2)
}

```

#### $\alpha_j$

```{r, fig.width = 6, fig.height = 4}
my_boxplot("alpha", latex2exp::TeX("$\\alpha_j$"), cols)
```

#### $S_{\mathrm{MSY},j}$

```{r, fig.width = 6, fig.height = 4}
my_boxplot("S_msy", latex2exp::TeX("$\\S_{MSY,j}\\,(000s)$"), cols, by_1000 = T)
```

#### $U_{\mathrm{MSY},j}$

```{r, fig.width = 6, fig.height = 4}
my_boxplot("U_msy", latex2exp::TeX("$\\U_{MSY,j}$"), cols)
```

#### $\phi_j$

```{r, fig.width = 6, fig.height = 4}
my_boxplot("phi", latex2exp::TeX("$\\phi_{j}$"), cols)
```

#### $\sigma_{R,j}$

```{r, fig.width = 6, fig.height = 4}
my_boxplot("sigma_R[", latex2exp::TeX("$\\sigma_{R,j}$"), cols)
```

### Spawner-Recruitment Relationships

Grey points are "fully-observed" spawner-recruitment pairs, i.e., escapement and harvest were monitored in each of the four years that recruits from a given brood year could return (depending on age), as well as in the year of spawning. Blue points are posterior medians of the latent state pairs -- only those brood years with a matching spawner abundance were used (i.e., the first 7 brood years are omitted). Arrows show the movement of the posteriors pairs off of the data pairs.

```{r SRA Plots, fig.height = 7, fig.width = 5}
# PLOT
a_post = log(post_subset(post, "alpha", matrix = T))
B_post = post_subset(post, "beta", matrix = T)
R = post_summ(post, "^R[")
R_med = array_format(R[3,])
R_lwr = array_format(R[4,])
R_upr = array_format(R[5,])
S = post_summ(post, "^S[")
S_med = array_format(S[3,])
S_lwr = array_format(S[4,])
S_upr = array_format(S[5,])

obs = gen_Rys_obs(params = params, obs = obs)

# spawner recruit plots
S_ind = 1:(nt - a_min)
R_ind = (a_max + 1):ny
s = 1
my_par(mfrow = c(4,2), mar = c(1.5,1.5,2,1), oma = c(2,2,0,0))
for (s in 1:ns) {
  # R.lim = c(0, max(c(R.mean[R.ind,s], R.mat[R.ind,s]), na.rm = T))
  # S.lim = c(0, max(c(S.mean[S.ind,s], S.ts[S.ind,s]), na.rm = T))
  R_lim = c(0, max(R_med[R_ind,s], obs$R_ys_obs[R_ind,s], na.rm = T))/1000
  S_lim = c(0, max(S_med[S_ind,s], obs$S_ts_obs[S_ind,s], na.rm = T))/1000
  S_range = seq(S_lim[1], S_lim[2], length = 100) * 1000
  
  pred_R_mat = mapply(function(a, B) S_range*exp(a - B * S_range), a_post[,s], B_post[,s])/1000
  pred_R = apply(pred_R_mat, 1, function(x) c(mean = mean(x), quantile(x, c(0.025, 0.975))))
  S_range = S_range/1000
  
  plot(1,1, type = "n", xlim = S_lim, ylim = range(R_lim, max(pred_R[3,])), main = stocks[s], las = 1)
  
  polygon(x = c(rev(S_range), S_range), y = c(rev(pred_R[3,]), pred_R[2,]), border = NA, col = cols$transparent)
  lines(pred_R[1,] ~ S_range, lwd = 3, col = cols$solid)
  lines(pred_R[2,] ~ S_range, col = cols$solid)
  lines(pred_R[3,] ~ S_range, col = cols$solid)
  
  points(I(obs$R_ys_obs[R_ind,s]/1000) ~ I(obs$S_ts_obs[S_ind,s]/1000),
         pch = 21, bg = scales::alpha("grey50", 0.5), col = scales::alpha("grey50", 0.75), cex = 1.5)
  points(I(R_med[R_ind,s]/1000) ~ I(S_med[S_ind,s]/1000),
         pch = 21, bg = cols$transparent, col = scales::alpha(cols$solid, 0.75), cex = 1.5)
  arrows(obs$S_ts_obs[S_ind,s]/1000, obs$R_ys_obs[R_ind,s]/1000, S_med[S_ind,s]/1000, R_med[R_ind,s]/1000, col = scales::alpha("grey50", 0.75), length = 0.05)
  abline(0,1, col = "grey", lty = 2)
}

mtext(side = 1, outer = T, "Spawners (000s)", line = 0.9)
mtext(side = 2, outer = T, "Recruits (000s)", line = 0.8)
```

### Fit to Data {.tabset .tabset-pills}

#### Escapement

```{r Spawner Time Series, fig.height = 7, fig.width = 5}
S = post_summ(post, "^S[")
S_med = array_format(S[3,])/1000
S_lwr = array_format(S[4,])/1000
S_upr = array_format(S[5,])/1000

my_par(mfrow = c(4,2), mar = c(1.5,1.5,2,1), oma = c(2,2,0,0))
for (s in 1:ns) {
  plot(S_med[,s] ~ years, type = "l", col = "black", lwd = 2, ylim = range(c(S_lwr[,s], S_upr[,s], obs$S_ts_obs[,s]/1000), na.rm = T), main = stocks[s], las = 1)
  polygon(x = c(rev(years), years), y = c(rev(S_lwr[,s]), S_upr[,s]), col = cols$transparent, border = NA)
  lines(S_lwr[,s] ~ years, col = cols$solid)
  lines(S_upr[,s] ~ years, col = cols$solid)
  lines(S_med[,s] ~ years, col = cols$solid, lwd = 2)
  points(I(obs$S_ts_obs[,s]/1000) ~ years, pch = 21, bg = "black", col = "black", cex = 1.5)
}
mtext(side = 1, outer = T, "Year", line = 0.9)
mtext(side = 2, outer = T, "Population-Specific Escapement (000s)", line = 0.8)

```

#### Harvest {.tabset .tabset-pills}

##### By Population

Note that this is the scale the models were fitted on.

```{r, fig.width = 5, fig.height = 7}
obs$C_ts_obs = apply(obs$S_ts_obs, 2, function(S) (S * obs$U_t_obs)/(1 - obs$U_t_obs))

C = post_summ(post, "^C[")
C_med = array_format(C[3,])/1000
C_lwr = array_format(C[4,])/1000
C_upr = array_format(C[5,])/1000

my_par(mfrow = c(4,2), mar = c(1.5,1.5,2,1), oma = c(2,2,0,0))
for (s in 1:ns) {
  plot(C_med[,s] ~ years, type = "l", col = "black", lwd = 2, las = 1, ylim = range(c(C_lwr[,s], C_upr[,s], obs$C_ts_obs[,s]/1000), na.rm = T), main = stocks[s])
  polygon(x = c(rev(years), years), y = c(rev(C_lwr[,s]), C_upr[,s]), col = cols$transparent, border = NA)
  lines(C_lwr[,s] ~ years, col = cols$solid)
  lines(C_upr[,s] ~ years, col = cols$solid)
  lines(C_med[,s] ~ years, col = cols$solid, lwd = 2)
  points(I(obs$C_ts_obs[,s]/1000) ~ years, pch = 21, bg = "black", col = "black", cex = 1.5)
}
mtext(side = 1, outer = T, "Year", line = 0.9)
mtext(side = 2, outer = T, "Population-Specific Harvest (000s)", line = 0.8)
```

##### Aggregate Population

Note that this is the scale the data are observed on, so it is informative to see how well the sum of population-specific fits match up with it. To obtain population-specific harvest values to fit to, we assumed all populations had exploitation rates equal to that observed for the aggregate population ($U_{y,o}$), and obtained observed harvest for each population ($H_{y,j,o}$) as:

\begin{equation}
H_{y,j,o} = \frac{S_{y,j,o} - U_{y,o}}{1 - U_{y,o}}
(\#eq:get-Hj-obs)
\end{equation}

```{r Harvest fit, fig.width = 6, fig.height = 4}
C_stock = post_subset(post, "^C", matrix = T)
C_tot_post = t(sapply(1:post_dim(post, "saved"), function(i) rowSums(array_format(C_stock[i,]))))
colnames(C_tot_post) = paste0("C_tot[", 1:35, "]")
post = post_bind(post, C_tot_post)

C_tot = post_summ(post, "C_tot[")/1000

my_par()
plot(C_tot[3,] ~ years, type = "l", las = 1, ylim = c(0, max(c(C_tot[5,], obs$C_tot_t_obs/1000))), xlab = "Year", ylab = "Aggregate Population Harvest (000s)")
polygon(x = c(years, rev(years)), y = c(C_tot[4,], rev(C_tot[5,])), col = "grey90", border = NA)
lines(C_tot[4,] ~ years, col = cols$solid)
lines(C_tot[5,] ~ years, col = cols$solid)
lines(C_tot[1,] ~ years, lwd = 2, col = cols$solid)
points(I(obs$C_tot_t_obs/1000) ~ years, pch = 21, bg = "black", col = "black", cex = 1.5)
```

#### Age Composition {.tabset .tabset-pills}

In these figures, the empty circles points represent years in which the model was fitted to data sampled from the aggregate population and filled points represent population-specific samples.

```{r age-comp-plots-ss-age}
age_plot_fun = function(s) {
  my_par(mfrow = c(2,2), mar = c(1,1,1.5,1), oma = c(2,2,0,0), cex.axis = 0.8)
  
  q_obs = matrix(NA, nrow(obs$x_tas_obs), ncol = ncol(obs$x_tas_obs))
  type = rep(NA, nrow(q_obs))
  
  for (t in 1:nrow(q_obs)) {
    if (is.na(obs$x_tas_obs[t,1,s+1])) {
      q_obs[t,] = obs$x_tas_obs[t,,1]
      type[t] = "agg"
    } else {
      q_obs[t,] = obs$x_tas_obs[t,,s+1]
      type[t] = "ss"
    }
  }
  
  q_obs = t(apply(q_obs, 1, function(x) x/sum(x)))
  q_fit = post_summ(post, paste0("q_stock[.+,.,", s, "]"))
  q_med = array_format(q_fit["50%",])[,,s]
  q_lwr = array_format(q_fit["2.5%",])[,,s]
  q_upr = array_format(q_fit["97.5%",])[,,s]
  
  ages = 4:7
  for (a in 1:na) {
    plot(q_med[,a] ~ years, type = "l",
         ylim = range(c(q_obs[,a], q_lwr[,a], q_upr[,a]), na.rm = T),
         main = paste("Age", ages[a]), las = 1)
    polygon(x = c(years, rev(years)), 
            y = c(q_lwr[,a], rev(q_upr[,a])), col = cols$transparent, border = NA)
    lines(q_lwr[,a] ~ years, col = cols$solid)
    lines(q_upr[,a] ~ years, col = cols$solid)
    lines(q_med[,a] ~ years, col = cols$solid, lwd = 2)
    points(q_obs[,a] ~ years, pch = ifelse(type == "agg", 1, 16), cex = 1.5)
  }
  
  mtext(side = 1, outer = T, line = 1, "Year")
  mtext(side = 2, outer = T, line = 1, "Age Composition")
}

```

`r s = 1; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 2; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 3; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 4; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 5; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 6; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 7; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

`r s = 8; paste("#####", stocks[s])`

```{r}
age_plot_fun(s)
```

#### Recruitment

**NOTE:** The state-space model does not fit to recruitment.
It reconstructs recruitment internally by fitting true latent states in the calendar years to observed states of escapement by population, aggregate harvest, and age composition if available.
This plot is included only to illustrate how well the model's reconstructions match one rational way of doing it external to the model.

```{r Recruitment Time Series, fig.width = 5, fig.height = 7}
R = post_summ(post, "^R[")
R_med = array_format(R[3,])/1000
R_lwr = array_format(R[4,])/1000
R_upr = array_format(R[5,])/1000

my_par(mfrow = c(4,2), mar = c(1.5,1.5,2,1), oma = c(2,2,0,0))
for (s in 1:ns) {
  plot(R_med[,s] ~ brood_years, type = "l", col = "black", lwd = 2, ylim = range(c(R_lwr[,s], R_upr[,s]), na.rm = T), main = stocks[s], las = 1)
  polygon(x = c(rev(brood_years), brood_years), y = c(rev(R_lwr[,s]), R_upr[,s]), col = cols$transparent, border = NA)
  lines(R_lwr[,s] ~ brood_years, col = cols$solid)
  lines(R_upr[,s] ~ brood_years, col = cols$solid)
  lines(R_med[,s] ~ brood_years, lwd = 2, col = cols$solid)
  points(I(obs$R_ys_obs[,s]/1000) ~ brood_years, pch = 21, bg = "black", col = "black", cex = 1.5)
}
mtext(side = 1, outer = T, "Brood Year", line = 0.9)
mtext(side = 2, outer = T, "Recruitment (000s)", line = 0.8)

```

### Recruitment Residuals

This figure shows the 8 population-specific recruitment residual time series ($v_{y,j}$) as thin lines and the average across populations as the heavy line.

```{r Recruitment Residuals, fig.height = 4, fig.width = 6}
log_resid = array_format(post_summ(post, "log_resid[")[3,])
mean_resid = rowMeans(log_resid)
max_resid = max(abs(log_resid))
my_par()
plot(mean_resid ~ brood_years, type = "n", ylim = c(-max_resid, max_resid), las = 1, xlab = "Brood Year", ylab = "log(Recruitment Residual)")
for (s in 1:ns) {lines(log_resid[,s] ~ brood_years, col = cols$transparent)}
lines(mean_resid ~ brood_years, lwd = 3, col = cols$solid)
```

### Trade-offs {.tabset .tabset-pills}

These relationships are posterior summaries of the aggregate population (the total of all 8 populations) under specific equilibrium conditions:

1.  There is no recruitment or maturation process variability (all $v_{y,j}$ are 0)
2.  All populations are fished at equal exploitation rates.
3.  The same exploitation rate is used year after year.

The equilibrium calculation for population-specific escapement ($S_{\mathrm{eq},j}$) at a fixed exploitation rate ($U_{\mathrm{eq}}$) is:

\begin{equation}
S_{\mathrm{eq},j} = S_{\mathrm{MSY},j} \frac{U_{\mathrm{MSY},j} - \ln\left(\frac{1 - U_{\mathrm{MSY},j}}{1 - U_{\mathrm{eq}}}\right)}{U_{\mathrm{MSY},j}}
(\#eq:get-Seq)
\end{equation}

and for equilibrium harvest ($H_{\mathrm{eq},j}$):

\begin{equation}
H_{\mathrm{eq},j} = \frac{U_{\mathrm{eq}}S_{\mathrm{eq},j}}{1 - U_{\mathrm{eq}}}
(\#eq:get-Heq)
\end{equation}

To build the trade-off relationships, we varied the equilibrium exploitation rate, performed the calculations on each population, and then summarized quantities across populations, e.g., summing population-specific harvest to obtain an estimate of aggregate harvest. This is an effective way to estimate the escapement ($S_{\mathrm{MSY}}$) or exploitation rate ($U_{\mathrm{MSY}}$) at maximum sustained yield from the aggregate population. Contrary to what one might expect, these quantities are not the simple summation or average of the individual population-specific quantities ($S_{\mathrm{MSY},j}$ and $U_{\mathrm{MSY},j}$). Instead, the shape of the trade-off relationships depends on the relationship between productivity and population size.

We define a population as being overfished if $U_{\mathrm{eq}} \gt U_{\mathrm{MSY},j}$ and extirpated if $S_{\mathrm{eq},j} \le 0$. At a given $U_{\mathrm{eq}}$, we calculated the proportion of populations for which these criteria were true as a way to measure risks to population diversity at different levels of exploitation.

The trade-off relationships are shown in two ways, where the x-axis represents either:

-   the equilibrium exploitation rate, which is applied to all populations equally, where the vertical line shows $U_{\mathrm{MSY}}$ and the horizontal line shows the aggregate population summary at that value
-   posterior median equilibrium escapement (obtained by applying an equilibrium exploitation rate to all populations equally) where the vertical line shows $S_{\mathrm{MSY}}$ and the horizontal line shows the aggregate population summary at that value


```{r Tradeoff Plot Calculations}

U.range = seq(0, 1, 0.01)

# function to find which element of x is closest to y
which_closest = function(x, y) {
  which.min(abs(x - y))
}

eq.ricker = function(U_msy, S_msy) {
  
  Seq = ((U_msy - log((1 - U_msy)/(1 - U.range)))/U_msy) * S_msy
  Seq[Seq < 0] = 0
  
  Ceq = (U.range * Seq)/(1 - U.range)
  Ceq[is.na(Ceq)] = 0
  Ceq[Ceq < 0] = 0

  overfished = ifelse(U.range > U_msy, 1, 0)
  extinct = ifelse(Seq == 0, 1, 0)

  return(list(S = Seq, C = Ceq, overfished = overfished, extinct = extinct))

}

# a.post = sort.post(post, "a[", do.post = T)$posterior
# b.post = sort.post(post, "B[", do.post = T)$posterior

U.msy.post = post_subset(post, "U_msy", matrix = T)
S.msy.post = post_subset(post, "S_msy", matrix = T)

n.saved = nrow(post[[1]] * length(post))
ni = min(n.saved, 5000)

n.U.range = length(U.range)
samp.i = sample(size = ni, x = 1:n.saved, replace = F)

S.out = array(NA, dim = c(n.U.range,ni, ns))
C.out = array(NA, dim = c(n.U.range, ni, ns))
overfished.out = array(NA, dim = c(n.U.range, ni, ns))
extinct.out = array(NA, dim = c(n.U.range, ni, ns))

S.tot = matrix(NA, n.U.range, ni)
C.tot = matrix(NA, n.U.range, ni)
p.overfished = matrix(NA, n.U.range, ni)
p.extinct = matrix(NA, n.U.range, ni)

for (i in 1:ni) {
  for (s in 1:ns) {
    
    temp = eq.ricker(U_msy = U.msy.post[samp.i[i],s], S_msy = S.msy.post[samp.i[i],s])
    
    S.out[,i,s] = temp$S
    C.out[,i,s] = temp$C
    overfished.out[,i,s] = temp$overfished
    extinct.out[,i,s] = temp$extinct
  }
  
  S.tot[,i] = rowSums(S.out[,i,])
  C.tot[,i] = rowSums(C.out[,i,])
  p.overfished[,i] = rowSums(overfished.out[,i,])/ns
  p.extinct[,i] = rowSums(extinct.out[,i,])/ns
}

S.tot.summ = apply(S.tot, 1, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
C.tot.summ = apply(C.tot, 1, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
overfished.summ = apply(p.overfished, 1, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
extinct.summ = apply(p.extinct, 1, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
```

```{r tradeoff_plot function}

# summ = overfished.summ
# against = "S"
# ylab = "Escapement"
# col = c("black", "grey90")
# # col = c("royalblue", scales::alpha("salmon", 0.5))

tradeoff_plot = function(summ, against = "U", ylab, add = F, legend = T, central = "50%", p_msy = 1, by_1000 = F) {
  my_par(xaxs = "i", yaxs = "i")
  
  xlab = ifelse(against == "U", "Exploitation Rate", "Escapement (000s)")
  
  if (against == "U") {
    at_x = U.range
  } else {
    at_x = S.tot.summ["50%",]/1000
  }
  
  if (by_1000) summ = summ/1000
  
  if (!add) {
    plot(1,1, type = "n", xlab = xlab, ylab = ylab, xlim = range(at_x), ylim = c(0, max(summ["97.5%",])) * 1.01, las = 1)
  }
  
  polygon(x = c(at_x, rev(at_x)), y = c(summ[4,], rev(summ[5,])), col = cols$transparent, border = NA)
  lines(summ[4,] ~ at_x, col = cols$solid)
  lines(summ[5,] ~ at_x, col = cols$solid)
  lines(summ[central,] ~ at_x, col = cols$solid, lwd = 4)
  
  msy = max(C.tot.summ["50%",]) * p_msy
  msy_inds = sapply(msy, function(y) which_closest(C.tot.summ["50%",], y))
  
  x_msy = at_x[msy_inds]
  y_msy = summ[central,msy_inds]
  segments(x_msy, 0, x_msy, y_msy, col = cols$solid, lty = c(2), lwd = 2)
  segments(0, y_msy, x_msy, y_msy, col = cols$solid, lty = c(2), lwd = 2)
  box()
}
```

#### X-axis: Exploitation Rate {.tabset .tabset-pills}

##### Escapement

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(S.tot.summ, "U", "Equilibrium Escapement (000s)", by_1000 = T)
```

##### Harvest

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(C.tot.summ, "U", "Equilibrium Harvest (000s)", by_1000 = T)
```

##### Populations Overfished

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(overfished.summ, "U", "Proportion of Populations Overfished", central = "mean")
```

##### Populations Extirpated

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(extinct.summ, "U", "Proportion of Populations Extirpated", central = "mean")
```

#### X-axis: Eq. Escapement {.tabset .tabset-pills}

##### Harvest

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(C.tot.summ, "S", "Equilibrium Harvest (000s)", by_1000 = T)
```

##### Populations Overfished

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(overfished.summ, "S", "Proportion of Populations Overfished", central = "mean")
```

##### Populations Extirpated

```{r, fig.width = 6, fig.height = 4}
tradeoff_plot(extinct.summ, "S", "Proportion of Populations Extirpated", central = "mean")
```

### Posterior Summaries {.tabset .tabset-pills}

```{r post_summ_kable function}
post_summ_kable = function(param, row.names, digits = 2) {
  tab = t(post_summ(post, param, digits = digits))
  rownames(tab) = row.names
  kable(tab, format = kable_format, format.args = list(big.mark = ","), row.names = T) %>%
    kable_styling(full_width = F, bootstrap_options = c("condensed"))
}
```

#### $\alpha_j$

```{r}
post_summ_kable("alpha", stocks)
```

#### $U_{\mathrm{MSY},j}$

```{r}
post_summ_kable("U_msy", stocks)
```

#### $S_{\mathrm{MSY},j}$

```{r}
post_summ_kable("S_msy", stocks, digits = -2)
```

#### $\sigma_{R,j}$

```{r}
post_summ_kable("sigma_R", stocks)
```

#### $\phi_j$

```{r}
post_summ_kable("phi", stocks)
```

#### $D_j$

```{r}
post_summ_kable("D_sum", stocks)
```

#### $\boldsymbol{\pi}_{j}$ {.tabset .tabset-pills}

##### $\pi_{4,j}$

```{r}
post_summ_kable("pi[1,", stocks, 3)
```

##### $\pi_{5,j}$

```{r}
post_summ_kable("pi[2,", stocks, 3)
```

##### $\pi_{6,j}$

```{r}
post_summ_kable("pi[3,", stocks, 3)
```

##### $\pi_{7,j}$

```{r}
post_summ_kable("pi[4,", stocks, 3)
```

#### Mixed-Stock Reference Points {.tabset .tabset-pills}

The following tables represent various aggregate populations quantities at different levels of population overfishing.
For example, the $S^{*}_{p}$ table shows the equilibrium aggregate escapement at which $p$ \* 100% of populations would be expected to be overfished.

```{r Drainage-Wide Reference Point Calculations}
star.seq = seq(0.1, 0.9, 0.1)

S.star = matrix(NA, ni, length(star.seq))
U.star = S.star
C.star = S.star
for (i in 1:ni) {
  S.star[i,] = sapply(X = star.seq, FUN = function(x) S.tot[which_closest(p.overfished[,i], x),i])
  U.star[i,] = sapply(X = star.seq, FUN = function(x) U.range[which_closest(p.overfished[,i], x)])
  C.star[i,] = sapply(X = star.seq, FUN = function(x) C.tot[which_closest(p.overfished[,i], x),i])
}

S.star.summ = apply(S.star, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
U.star.summ = apply(U.star, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
C.star.summ = apply(C.star, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))


rownames(S.star.summ) = rownames(U.star.summ) = rownames(C.star.summ) = c("Mean", "SD", "Median", "2.5%", "97.5%")

S.star.summ = round(S.star.summ, -3)
C.star.summ = round(C.star.summ, -3)
U.star.summ = round(U.star.summ, 2)

S.star.summ = t(rbind(p = star.seq, S.star.summ[c(1,4,5),]))
C.star.summ = t(rbind(p = star.seq, C.star.summ[c(1,4,5),]))
U.star.summ = t(rbind(p = star.seq, U.star.summ[c(1,4,5),]))

```

##### $S^{*}_{p}$

```{r S.star Table}
kable(S.star.summ, format = kable_format, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  column_spec(1, bold = T)
```

##### $H^{*}_{p}$

```{r C.star Table}
kable(C.star.summ, format = kable_format, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  column_spec(1, bold = T)
```

##### $U^{*}_{p}$

```{r U.star Table}
kable(U.star.summ, format = kable_format, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  column_spec(1, bold = T)
```
