---
title: "Chinook salmon diversity contributes to fishery stability and trade-offs with mixed-stock harvest"
subtitle:  |
    | Ecological Applications
    | Appendix S2
author: "B.M. Connors, M. R. Siegle, J. Harding, S. Rossi, B.A. Staton, M.L. Jones, M. Bradford, R. Browne, B. Bechtol, B. Doherty, S. Cox, and B.J.G. Sutherland"
output: 
  bookdown::html_document2:
  # bookdown::word_document2:
    theme: cerulean
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: sentence
bibliography: references.bib
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/canadian-journal-of-fisheries-and-aquatic-sciences.csl"
link-citations: true
always_allow_html: yes
---

```{r setup, include = F}
# set chunk options
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.align = "center", dpi = 250)
kable_format = ifelse(knitr::is_html_output(), "html", "simple")
```

```{r my_par() function}
my_par = function(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15, ljoin = "mitre", lend = "square", ...) {
  par(mar = mar, mgp = mgp, tcl = tcl, ljoin = ljoin, lend = lend, ...)
}
```

This appendix provides a detailed description of the spawner-recruitment models that are briefly described in the main text and which were used to quantify Canadian-origin Yukon Chinook population diversity (e.g., population specific spawner abundance, recruitment, productivity, capacity, covariation in survival, etc.) and resulting portfolio effects and mixed-stock fishery trade-offs. 

# Primary Spawner-Recruitment Analysis: Population-Specific Models

The approach described in this section fits a separate spawner-recruitment model to each population, and summarizes the resulting parameter estimates for primary inference.
We also fitted a single multi-population spawner-recruitment model that estimates all population parameters simultaneously in an attempt to more realistically represent shared population dynamics and measurement processes, see the section [Alternative Method: Mixed-Population Model](#alt-ssm) for description and a comparison of approaches.

```{r, eval = T, child = "description-separated.Rmd"}
```

```{r, eval = T, child = "results-separated.Rmd"}
```

# Alternative Method: Mixed-Population Model {#alt-ssm}

```{r, eval = T, child = "description-integrated.Rmd"}
```

```{r, eval = T, child = "results-integrated.Rmd"}
```

# Conclusions

```{r, eval = T, child = "discussion.Rmd"}
```

# References
